``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)

### 2022-12-20 paper/04--otherLinearization.tex
further corrections

 \begin{figure}[h]
 	\caption{Example of Desired Additional Orderings}
 	\label{fig:OrderingRules}
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->, bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	}
\end{figure}

\begin{figure}[h]
	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
	\label{fig:CycleBreaking}
	\scalebox{0.75}{
		\begin{subfigure}{7cm}
		 	\centering
			\caption{Resulting method ordering has a cycle}
			\label{fig:CycleBreaking1}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

		\end{subfigure}
	}
\end{figure}

>>>>

 \begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->, bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	}
	 	\caption{Example of Desired Additional Orderings\label{fig:OrderingRules}}
\end{figure}

\begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{7cm}
		 	\centering
			\caption{Resulting method ordering has a cycle}
			\label{fig:CycleBreaking1}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}
		\end{subfigure}
	}
	\caption{Example of Cycle-Breaking the Desired Additional Orderings\label{fig:CycleBreaking}\Psays{Ying, captions come in figures always below the graphics. Can you fix this? The captions are also not self-explanatory. E.g. in (a) you mention 'resulting', but it's completely unclear what you are referring to. Caption (b) is also not self-explanatory.}}
\end{figure}

### 2022-12-20 paper/paper-mainfile.tex
further corrections

% % % % % PACKAGES IMPORTED BY US % % % % %
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathbbol}
\usepackage[noend]{algpseudocode}
\usepackage{paralist}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{aiplans}

@@

>>>>

% % % % % PACKAGES IMPORTED BY US % % % % %
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{todonotes}
% \usepackage{mathbbol}
\usepackage[noend]{algpseudocode}
\usepackage{paralist}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{aiplans}

@@

\Psays{Ying, there are several unresolved references, can you please fix all of them? \includegraphics[width=\textwidth]{errors}}

\Psays{There are quote a range of 'typical' errors throughout, see the list below}
\begin{itemize}
  \item Your quotes are wrong. You have to always use `6/9', ``66/99'', not '9/9'
  \item Most citations are wrong. See my template for the rules.
  \item You cite a paper by Erol twice, please fix (and remove the duplicate reference)
  \item Gregor's AAAI'22 is missing page numbers.
  \item Sometimes you have a dot that's not ending a sentence, yet you don't protect the next whitespace (see my template for an explanation)
\end{itemize}
